Security performance in the Android ecosystem

### 2015-06-03 ccs.tex
comment out the Acknowledgments until we have some
update contributions

\todo{continue here}
In summary, the contributions of this paper are:
\begin{itemize}
 \item We measure the security of Android according to three metrics and compare different device manufacturers and device models to allow device purchasers to differentiate between them based on security.
\end{itemize}

@@

\identifying{
\section*{Acknowledgements}
}

>>>>

In summary, the contributions of this paper are:
\begin{itemize}
 \item We quantify the Android update process.
 \item We propose a scoring metric to evaluate the security of different instances of a platform.
 \item We measure the security of Android according to this and compare different device manufacturers, device models and network operators to allow device purchasers to differentiate between them based on security.
\end{itemize}

@@

\identifying{
%\section*{Acknowledgements}
}
